\documentclass{llncs} % , times

\usepackage{amssymb, amsmath, graphicx, ltxtable, longtable, tabularx, url, ragged2e, xspace, verbatim, fancybox,tikz}
\usepackage{scalefnt}
\usepackage{relsize}
\usepackage{hyperref}
%\usepackage{paralist}
%\usepackage{listings}

\newcommand{\ggr}[1]{\textcolor{magenta}{comment Gerd: \textit{#1}}}

\pagenumbering{arabic}
\pagestyle{plain}

\begin{document}
\title{Research Agenda --- Meeting 1 (July 24)}
 

\maketitle

\begin{abstract}
This document gives a short summary of the first meeting on
July 24, 2013.
The main topics are: research activity and 
\end{abstract}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Status Report}

I have decided to focus on \emph{software architectures} and especially
for \emph{Future Internet} systems.
The work was inspired by the LoFIP and FInest architectures.

\subsection{Achievements until now}

\begin{itemize}
	\item Basic definitions and terminology of software architectures (and views).
	\item Learning and comparing the LoFIP and FInest architectures.
	   \begin{itemize}
			 \item \textbf{Observations:} The LoFIP ``Leitstand'' architecture
			       and the FInest Core architecture do not show dedicated
						 constructs regarding the ``Future Internet''. 
						 IoT and IoS are (mainly) incorporated in the back end and front end.
		 \end{itemize}
\end{itemize}


\subsection{Next steps (until July 30)}

\begin{itemize}
	\item Look into the LoFIP components \emph{MONITOR} and \emph{ANALYZE} and
	  identify special aspects (or requirements) when data input, data output
		 and communication rely on IoT and IoS.
		For instance, typical aspects are uncertainty, delay, unavailability of services
		or inappropriate connections.
	\item Investigate the influence (or whether there is an influence at all) of user interactions
	   to the MAPE-K reference model. (MAPE-K, as a reference model for self-adaptive systems,
		 is adapted as a kind of blueprint for the ``Leitstand'' architecture in LoFIP.)
\end{itemize}


\section{Long-term Goal}

The focus of my research is on software architecture.
How does my background fit into this?
\begin{itemize}
	\item \textbf{Model-driven engineering:} Modeling, model transformation, alignment and mapping
	\item \textbf{Business process management:} From the architecture to the execution.
	   Two dimensions: process and architecture (structure) and they have to be ``synchronized'',
		  leading to problems like adaptation, exception handling, ad-hoc processes, monitoring, etc.
	\item \textbf{Knowledge representation:} Enrich architectures by knowledge bases (ontologies)
	  and apply reasoning for analyzing, planning and prioritizing actions.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{plain}
%\bibliography{bib-architecture}

\end{document}